---
title: "Test phase analysis"
doi: "https://doi.org/10.17605/OSF.IO/9TUZE"
author: "Milena Musial"
date: 08/03/2025
format: html
editor: visual
toc: TRUE
code-fold: TRUE
warning: FALSE
number-sections: TRUE
embed-resources: true
execute: 
  warning: FALSE
editor_options: 
  chunk_output_type: console
---

# Set up

```{r}
require(nothing, quietly = TRUE)
rm(list = ls(all = TRUE))

# Load packages
packages <- c("ggplot2", "tidyr", "kableExtra", "gmodels", "lme4", "sjPlot", "viridis", "forcats", "lmerTest", "car", "PerformanceAnalytics", "emmeans", "corrplot", "Hmisc", "performance", "MASS", "dplyr", "ggpubr", "robustlmm", "confintROB")
#install.packages(packages)
invisible(lapply(packages, require, character.only = TRUE))

# set color scheme
custom_colors <- viridis(5, option = "viridis")[c(1, 2, 3, 4, 5)]

# define paths
#data_path <- "~/work/group_folder/B01_FP2_WP3/WP3_DATA/FINAL_STUDY/RDFs"
data_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/WP3/WP3_DATA/FINAL_STUDY/RDFs"
model_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/WP3/WP3_DATA/FINAL_STUDY/model_objects"
figure_path <- "/Users/milenamusial/Library/CloudStorage/OneDrive-Charité-UniversitätsmedizinBerlin/PhD/04_B01/WP3/Project_Docs/Figures/behavioral"

# read dfs
load(file.path(data_path, "final_data_included.RData"))
load(file.path(data_path, "demo_psych_data_included.RData"))

# show all digits for emmeans comparisons
emm_options(opt.digits = FALSE)
```

# Main analysis

## Performance per condition, across groups and versions

```{r}

test_correct_paths_condition_df <- trial_df %>%
  filter(phase == "test",
         state %in% c(1)
         ) %>%
  group_by(condition) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )

test_correct_paths_condition_df %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")

test_correct_paths_group_version_condition_df <- trial_df %>%
  filter(phase == "test",
         state %in% c(1)
         ) %>%
  group_by(group, version, condition) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )

test_correct_paths_group_version_condition_df %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

## Plots

### Performance per condition, group, version

```{r}

test_correct_paths_group_version_condition_df <- trial_df %>%
  filter(phase == "test",
         state %in% c(1)
         ) %>%
  group_by(group, version, condition) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )

test_correct_paths_group_version_condition_df %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")

```

```{r}
# bar plot
supp.labs <- c("Low-risk drinkers", "High-risk drinkers", "Non-alcohol context", "Alcohol context")
names(supp.labs) <- c("Low-risk drinkers", "Harmful drinkers", "Monetary version", "Alcohol version")

ggplot(test_correct_paths_group_version_condition_df, aes(x=condition, y=mean_switch)) +
  geom_bar(stat="identity", aes(fill = condition)) +
  geom_errorbar(aes(ymin=mean_switch-se_switch, ymax=mean_switch+se_switch),
                width=.3,
                position=position_dodge(.9)) +
  facet_grid(vars(group), vars(version), labeller = as_labeller(supp.labs)) +
  scale_y_continuous("Proportion of test trials \n with changed path preference", limits = c(-0.05, 1.05)) +
  theme_light(base_size = 12, base_family = "Arial") +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 50, vjust = 1, hjust=1, size=12),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 12)) +
  scale_fill_viridis(option = "viridis", discrete = TRUE)

ggsave(filename = "main_revaluation_test.png", path = figure_path, width = 8.5, height = 6.5, device='png', dpi=600)
```

### Low-risk drinkers monetary version only

```{r}
test_correct_paths_lowrisk_mon_condition_df <- trial_df %>%
  filter(phase == "test",
         state %in% c(1),
         group == "Low-risk drinkers",
         version == "Monetary version"
         ) %>%
  group_by(condition) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )
```

```{r}
# bar plot
ggplot(test_correct_paths_lowrisk_mon_condition_df, aes(x=condition, y=mean_switch)) +
  geom_bar(stat="identity", aes(fill = condition)) +
  geom_errorbar(aes(ymin=mean_switch-se_switch, ymax=mean_switch+se_switch),
                width=.2,
                position=position_dodge(.9)) +
  scale_y_continuous("Proportion of test trials \n with changed path preference", limits = c(-0.05, 1.05)) +
  theme_light(base_size = 12, base_family = "Arial") +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 50, vjust = 1, hjust=1, size=12)) +
  scale_fill_viridis(option = "viridis", discrete = TRUE)

ggsave(filename = "main_lowrisk_monetary.png", path = figure_path, width = 5, height = 4.5, device='png', dpi=600)

```

### Histogram of individual differences in performance per condition, group, version

```{r}

test_correct_paths_group_version_condition_ID_df <- trial_df %>%
  filter(phase == "test",
         state %in% c(1)
         ) %>%
  group_by(group, version, condition, ID) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )

test_correct_paths_group_version_condition_ID_df %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")

```

```{r}

supp.labs <- c("Low-risk drinkers", "High-risk drinkers", "Non-alcohol context", "Alcohol context", "Reward revaluation", "Goal-state revaluation", "Transition revaluation", "Policy revaluation", "Control")
names(supp.labs) <- c("Low-risk drinkers", "Harmful drinkers", "Monetary version", "Alcohol version", "Reward revaluation", "Goal-state revaluation", "Transition revaluation", "Policy revaluation", "Control")

# bar plot
ggplot(test_correct_paths_group_version_condition_ID_df, aes(x=mean_switch, fill = condition, color=condition)) +
  geom_histogram(alpha = 0.5, position="identity", binwidth = 0.2) +
  facet_wrap(~ group + version + condition, nrow=4, labeller = as_labeller(supp.labs)) +
  scale_x_continuous(name = "Proportion of test trials with changed path preference", breaks = seq(0, 1, by = 0.2)) +
  scale_y_continuous(name = "Number of participants") +
  theme_light(base_size = 16, base_family = "Aptos") +
  theme(#axis.title.x = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16)) +
  scale_fill_viridis(option = "viridis", discrete = TRUE) +
  scale_color_viridis(option = "viridis", discrete = TRUE)

ggsave(filename = "suppl_revaluation_distribution.png", path = figure_path, width = 14, height = 12, device='png', dpi=600)
```

## Logistic regression

```{r}
# Set contrasts
contrasts(trial_df$group) <- contr.sum(2)*-0.5
contrasts(trial_df$version) <- contr.sum(2)*-0.5
### contrast for condition changes from analysis to analysis

# Prepare LogReg dfs
logreg_test_path_group_version_condition_df_full <- trial_df %>%
  filter(phase == "test",
         state == 1) %>%
  mutate(condition = as.factor(condition),
         version = as.factor(version),
         group = as.factor(group),
         environment = as.factor(environment)) %>%
  dplyr::select(group,
         version,
         ID,
         switch_path,
         condition,
         environment)

logreg_test_path_condition_df_lowrisk_control <- trial_df %>%
  filter(phase == "test",
         state == 1,
         group == "Low-risk drinkers",
         version == "Monetary version") %>%
  mutate(condition = as.factor(condition),
         environment = as.factor(environment)) %>%
  dplyr::select(ID,
         switch_path,
         condition,
         environment)

logreg_test_path_group_condition_df_alcohol <- trial_df %>%
  filter(phase == "test",
         state == 1,
         version == "Alcohol version") %>%
  mutate(condition = as.factor(condition),
         group = as.factor(group),
         environment = as.factor(environment)) %>%
  dplyr::select(group,
         ID,
         switch_path,
         condition,
         environment)

# Check contrasts
contrasts(logreg_test_path_group_version_condition_df_full$group)
contrasts(logreg_test_path_group_version_condition_df_full$version)
```

### ICC

```{r}
# Null model
m_icc <- glmer(switch_path ~
                  1 + (1 | ID),
                data = logreg_test_path_group_version_condition_df_full,
                family = "binomial",
                glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))

tab_model(m_icc, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

# Use alternative method to compare results
icc(m_icc)
```

### Model 1: Low-risk drinkers, control version, compare against transition revaluation

> **Hypothesis 1:** **Main effect of condition (reward vs. transition revaluation, goal-state vs. transition revaluation)**

> Low-risk drinkers use SR to some extent when learning in a non-alcohol context. Specifically, we expect more correct test phase paths in the reward revaluation and the goal-state revaluation conditions compared to the transition revaluation condition, respectively.

```{r}
contrasts(logreg_test_path_condition_df_lowrisk_control$condition) <- contr.treatment(5, base = 3)

#model1 <- glmer(switch_path ~ condition + (1 | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model1, file=file.path(model_path, "model1_switch.rds"))
model1 <- readRDS(file.path(model_path, "model1_switch.rds"))

#model1_rs <- glmer(switch_path ~ condition + (1 + condition | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model1_rs, file=file.path(model_path, "model1_rs_switch.rds"))
model1_rs <- readRDS(file.path(model_path, "model1_rs_switch.rds"))

anova(model1, model1_rs)

tab_model(model1_rs, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model1_rs, check=c("pp_check", "reqq", "qq"))
```

### Model 2: Low-risk drinkers, control version, compare against policy revaluation

> **Hypothesis 2:** **Main effect of condition (reward vs. policy revaluation, goal-state vs. policy revaluation)**

> The differences between reward and transition revaluation and between goal-state and transition revaluation cannot fully be explained by use of a model-based strategy with a higher learning rate for the reward compared to the transition structure. Specifically, we expect fewer correct test phase paths in the policy revaluation condition compared to the reward and goal-state revaluation conditions, respectively.

```{r}
contrasts(logreg_test_path_condition_df_lowrisk_control$condition) <- contr.treatment(5, base = 4)

# model2 <- glmer(switch_path ~ condition + (1 | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model2, file=file.path(model_path, "model2_switch.rds"))
model2 <- readRDS(file.path(model_path, "model2_switch.rds"))

# model2_rs <- glmer(switch_path ~ condition + (1 + condition | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model2_rs, file=file.path(model_path, "model2_rs_switch.rds"))
model2_rs <- readRDS(file.path(model_path, "model2_rs_switch.rds"))

anova(model2, model2_rs)

tab_model(model2_rs, show.est = T, show.stat = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model2_rs, check=c("pp_check", "reqq", "qq"))
```

#### Did individuals who explored more during learning phase perform better in policy revaluation (more positive slopes policy vs. transition)?

```{r}
# get fixed effects
fixed_effects <- fixef(model1_rs) 

# extract individual slopes for condition (contrast policy vs. transition)
random_slopes <- ranef(model1_rs)$ID[,4]

# calculate individual adjusted slopes for condition (contrast reward vs. policy)
individual_slopes <- fixed_effects["condition4"] + random_slopes  # Add individual deviations

# calculate how often suboptimal path was taken during learning
exploration_df <- trial_df %>%
  filter(group == "Low-risk drinkers",
         version == "Monetary version",
         condition == "Policy revaluation",
         phase == "learning") %>%
  filter(! trial %in% c(1,2,3,4)) %>%
  group_by(ID, trial) %>%
  mutate(least_optimal_path = case_when((state == 1 & correct == 0 & lead(correct) == 0) ~ 1, # incorrect state 1 and second stage choice
                                  (state == 1 & correct == 1) ~ 0, # correct state 1 choice
                                  (state == 1 & lead(correct) == 1) ~ 0), # correct second stage choice
         suboptimal_path = case_when((state == 1 & correct == 0) ~ 1, # incorrect state 1 choice
                                  (state == 1 & lead(correct) == 0) ~ 1, # incorrect second stage choice
                                  (state == 1 & correct == 1 & lead(correct) == 1) ~ 0,)) %>%  # correct state 1 and incorrect second stage choice)
  filter(state == 1) %>%
  group_by(ID) %>%
  mutate(percent_least_optimal_path = mean(least_optimal_path),
         percent_exploration = mean(suboptimal_path)) %>%
  dplyr::select(ID, percent_least_optimal_path, percent_exploration) %>%
  unique() %>%
  arrange(ID)

exploration_df$individual_slope <- individual_slopes

mean(exploration_df$percent_least_optimal_path)
sd(exploration_df$percent_least_optimal_path, na.rm = TRUE)/sqrt(nrow(exploration_df))
                                                  
cor.test(exploration_df$percent_least_optimal_path, exploration_df$individual_slope, method="spearman", exact=F)
#cor.test(exploration_df$percent_exploration, exploration_df$individual_slope)

ggplot(exploration_df, aes(x=percent_least_optimal_path, y=individual_slope)) +
  geom_jitter(aes(y=individual_slope), size=2, color="black", width = 0.002) +
  geom_smooth(method = 'lm', alpha = 0.2, size=1.3, color="black") + 
  scale_y_continuous("Individual slope \n policy > transition revaluation") +
  scale_x_continuous("Proportion of \n least optimal path choices \n in policy revaluation learning phase") +
  theme_light(base_size = 12, base_family = "Arial")

ggsave(filename = "main_policy_correlation.png", path = figure_path, width = 4, height = 4.5, device='png', dpi=600)

```

### Model 1/2 explo: Low-risk drinkers, control version, compare against reward revaluation

```{r}
contrasts(logreg_test_path_condition_df_lowrisk_control$condition) <- contr.treatment(5, base = 1)

# model12explo <- glmer(switch_path ~ condition + (1 | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model12explo, file=file.path(model_path, "model12explo_switch.rds"))
model12explo <- readRDS(file.path(model_path, "model12explo_switch.rds"))

# model12explo_rs <- glmer(switch_path ~ condition + (1 + condition | ID), data = logreg_test_path_condition_df_lowrisk_control, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model12explo_rs, file=file.path(model_path, "model12explo_rs_switch.rds"))
model12explo_rs <- readRDS(file.path(model_path, "model12explo_rs_switch.rds"))

anova(model12explo, model12explo_rs)

tab_model(model12explo_rs, show.est = T, show.stat = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model2_rs, check=c("pp_check", "reqq", "qq"))
```

### Model 3: Full dataset, compare against transition revaluation

> **Hypothesis 3:** **Interaction of condition (reward vs. transition revaluation) \* group (harmful vs. low-risk drinkers)**

> Individuals with harmful alcohol use (harmful drinkers) show a higher degree of SR use compared to individuals with low-risk alcohol use (low-risk drinkers). Specifically, we expect more correct test phase paths in the reward revaluation condition compared to the transition revaluation condition for harmful drinkers compared to low-risk drinkers.

> **Hypothesis 4:** **Interaction of condition (reward vs. transition revaluation) \* group (harmful vs. low-risk drinkers) \* context (alcohol vs. non-alcohol)**

> Harmful drinkers show a higher degree of SR use compared to low-risk drinkers when learning in an alcohol compared to a non-alcohol context. Specifically, we expect more correct test phase paths in the reward revaluation compared to the transition revaluation condition for harmful drinkers compared to low-risk drinkers in the alcohol compared to the non-alcohol task version.

```{r}
contrasts(logreg_test_path_group_version_condition_df_full$condition) <- contr.treatment(5, base = 3)

# model3_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model3_vers, file=file.path(model_path, "model3_vers_switch.rds"))
model3_vers <- readRDS(file.path(model_path, "model3_vers_switch.rds"))

# model3_rs_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 + condition | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model3_rs_vers, file=file.path(model_path, "model3_rs_vers_switch.rds"))
model3_rs_vers <- readRDS(file.path(model_path, "model3_rs_vers_switch.rds"))

anova(model3_vers, model3_rs_vers)

tab_model(model3_rs_vers, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model3_rs_vers, check=c("pp_check", "reqq", "qq"))
```

#### Inspect interactions

```{r}
# get marginal means per version
mmeans <- emmeans(model3_rs_vers, specs = ~ condition|version, ref="Transition revaluation", type="response")
mmeans

# contrasts between marginal means per group and version
contrasts <- contrast(mmeans,
                      list(reward_transition = c(1, 0, -1, 0, 0),
                           goalstate_transition = c(0, 1, -1, 0, 0),
                           policy_transition = c(0, 0, -1, 1, 0)),
                      adjust = "bonferroni")
contrasts
```

#### Did individuals who explored more during learning phase perform better in policy revaluation (more positive slopes)?

```{r}
# load model
model3_rs_vers <- readRDS(file.path(model_path, "model3_rs_vers_switch.rds"))

# get fixed effects
fixed_effects <- fixef(model3_rs_vers)

# extract individual slopes for condition (contrast policy vs. transition)
random_slopes <- ranef(model3_rs_vers)$ID[,"condition4"]

# create binary group and version variables
dummies <- demo_psych %>%
  arrange(prolific_ID) %>%
  mutate(group_binary = ifelse(group == "Harmful drinkers", 0.5, -0.5),
         version_binary = ifelse(version == "Alcohol version", 0.5, -0.5)) %>%
  dplyr::select(group_binary, version_binary)

# calculate individual adjusted slopes for condition (contrast reward vs. transition)
individual_slopes <- fixed_effects["condition4"] +  # Main effect of condition 1
                    fixed_effects["group1:condition4"] * dummies$group_binary +  # Adjust for group interaction
                    fixed_effects["version1:condition4"] * dummies$version_binary +  # Adjust for version interaction
                    fixed_effects["group1:version1:condition4"] * (dummies$group_binary * dummies$version_binary) +  # Three-way interaction
                    random_slopes  # Add individual deviations

# calculate how often suboptimal path was taken during learning
exploration_df <- trial_df %>%
  filter(condition == "Policy revaluation",
         phase == "learning") %>%
  filter(! trial %in% c(1,2,3,4)) %>%
  group_by(ID, trial) %>%
  mutate(least_optimal_path = case_when((state == 1 & correct == 0 & lead(correct) == 0) ~ 1, # incorrect state 1 and second stage choice
                                  (state == 1 & correct == 1) ~ 0, # correct state 1 choice
                                  (state == 1 & lead(correct) == 1) ~ 0), # correct second stage choice
         suboptimal_path = case_when((state == 1 & correct == 0) ~ 1, # incorrect state 1 choice
                                  (state == 1 & lead(correct) == 0) ~ 1, # incorrect second stage choice
                                  (state == 1 & correct == 1 & lead(correct) == 1) ~ 0,)) %>%  # correct state 1 and incorrect second stage choice)
  filter(state == 1) %>%
  group_by(ID) %>%
  mutate(percent_least_optimal_path = mean(least_optimal_path),
         percent_exploration = mean(suboptimal_path)) %>%
  dplyr::select(ID, percent_least_optimal_path, percent_exploration) %>%
  unique() %>%
  arrange(ID)

exploration_df$individual_slope <- individual_slopes

mean(exploration_df$percent_least_optimal_path)
sd(exploration_df$percent_least_optimal_path, na.rm = TRUE)/sqrt(nrow(exploration_df))
                                                  
cor.test(exploration_df$percent_least_optimal_path, exploration_df$individual_slope, method="spearman", exact=F)
#cor.test(exploration_df$percent_exploration, exploration_df$individual_slope)

ggplot(exploration_df, aes(x=percent_least_optimal_path, y=individual_slope)) +
  geom_jitter(aes(y=individual_slope), size=2, color="black", width = 0.002) +
  geom_smooth(method = 'lm', alpha = 0.2, size=1.3, color="black") + 
  scale_y_continuous("Individual slope \n policy > transition revaluation") +
  scale_x_continuous("Proportion of \n least optimal path choices \n in policy revaluation learning phase") +
  theme_light(base_size = 16, base_family = "Arial")

ggsave(filename = "main_policy_correlation_all.png", path = figure_path, width = 5, height = 5.5, device='png', dpi=600)

```

### Model 4: Alcohol context, compare against reward revaluation

> **Hypothesis 5: Interaction of condition (goal-state vs. reward revaluation) \* group (harmful vs. low-risk drinkers)**

> Harmful drinkers show a higher degree of rigid goal-based reduced SR use when learning in an alcohol context compared to low-risk drinkers. Specifically, we expect less correct test phase paths in the goal-state compared to the reward revaluation condition for harmful drinkers compared to low-risk drinkers.

```{r}
contrasts(logreg_test_path_group_condition_df_alcohol$condition) <- contr.treatment(5, base = 1)

# model4 <- glmer(switch_path ~ condition*group + (1 | ID), data = logreg_test_path_group_condition_df_alcohol, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model4, file=file.path(model_path, "model4_switch.rds"))
model4 <- readRDS(file.path(model_path, "model4_switch.rds"))

# model4_rs <- glmer(switch_path ~ condition*group + (1 + condition | ID), data = logreg_test_path_group_condition_df_alcohol, family = "binomial", glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model4_rs, file=file.path(model_path, "model4_rs_switch.rds"))
model4_rs <- readRDS(file.path(model_path, "model4_rs_switch.rds"))

anova(model4, model4_rs)

tab_model(model4_rs, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model4_rs, check=c("pp_check", "reqq", "qq"))
```

### Model 5: Full dataset, compare against reward revaluation

> **Hypothesis 6: Interaction of condition (goal-state vs. reward revaluation) \* group (harmful vs. low-risk drinkers) \* context (alcohol vs. non-alcohol)**

> Harmful drinkers show a higher degree of rigid goal-based reduced SR use compared to low-risk drinkers when learning in an alcohol compared to a non-alcohol context. Specifically, we expect less correct test phase paths in the goal-state compared to the reward revaluation condition for harmful drinkers compared to low-risk drinkers in the alcohol compared to the non-alcohol task version.

```{r}
contrasts(logreg_test_path_group_version_condition_df_full$condition) <- contr.treatment(5, base = 1)

# model5_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model5_vers, file=file.path(model_path, "model5_vers_switch.rds"))
model5_vers <- readRDS(file.path(model_path, "model5_vers_switch.rds"))

# model5_rs_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 + condition | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model5_rs_vers, file=file.path(model_path, "model5_rs_vers_switch.rds"))
model5_rs_vers <- readRDS(file.path(model_path, "model5_rs_vers_switch.rds"))

anova(model5_vers, model5_rs_vers)

tab_model(model5_rs_vers, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model5_rs_vers, check=c("pp_check", "reqq", "qq"))
```

#### Inspect interactions

```{r}
# get marginal means per group
mmeans <- emmeans(model5_rs_vers, specs = ~ condition|group, ref="Reward revaluation", type="response")
mmeans

# contrasts between marginal means per group
contrasts <- contrast(mmeans, 
                      list(goalstate_reward = c(-1, 1, 0, 0, 0),
                           control_reward = c(-1, 0, 0, 0, 1)),
                      adjust = "bonferroni")
contrasts

# get marginal means per version
mmeans <- emmeans(model5_rs_vers, specs = ~ condition|version, ref="Reward revaluation", type="response")
mmeans

# contrasts between marginal means per version
contrasts <- contrast(mmeans, 
                      list(transition_reward = c(-1, 0, 1, 0, 0),
                           control_reward = c(-1, 0, 0, 0, 1)),
                      adjust = "bonferroni")
contrasts
```

### Compare to control condition

#### Low-risk drinkers, control context

```{r}

contrasts(logreg_test_path_condition_df_lowrisk_control$condition) <- contr.treatment(5, base = 5)

# model1_control_vers <- glmer(switch_path ~
#                   condition +
#                   (1 | ID),
#                 data = logreg_test_path_condition_df_lowrisk_control,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model1_control_vers, file=file.path(model_path, "model1_control_vers_switch.rds"))
model1_control_vers <- readRDS(file.path(model_path, "model1_control_vers_switch.rds"))

# model1_control_rs_vers <- glmer(switch_path ~
#                   condition +
#                   (1 + condition | ID),
#                 data = logreg_test_path_condition_df_lowrisk_control,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model1_control_rs_vers, file=file.path(model_path, "model1_control_rs_vers_switch.rds"))
model1_control_rs_vers <- readRDS(file.path(model_path, "model1_control_rs_vers_switch.rds"))

anova(model1_control_vers, model1_control_rs_vers)

tab_model(model1_control_rs_vers, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model1_control_rs_vers, check=c("pp_check", "reqq", "qq"))
```

#### Full sample

```{r}
contrasts(logreg_test_path_group_version_condition_df_full$condition) <- contr.treatment(5, base = 5)

# model3_control_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model3_control_vers, file=file.path(model_path, "model3_control_vers_switch.rds"))
model3_control_vers <- readRDS(file.path(model_path, "model3_control_vers_switch.rds"))

# model3_control_rs_vers <- glmer(switch_path ~
#                   group*version*condition +
#                   (1 + condition | ID),
#                 data = logreg_test_path_group_version_condition_df_full,
#                 family = "binomial",
#                 glmerControl(optCtrl=list(maxfun=1e6),
#                              optimizer = "bobyqa"))
# saveRDS(model3_control_rs_vers, file=file.path(model_path, "model3_control_rs_vers_switch.rds"))
model3_control_rs_vers <- readRDS(file.path(model_path, "model3_control_rs_vers_switch.rds"))

anova(model3_control_vers, model3_control_rs_vers)

tab_model(model3_control_rs_vers, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model3_control_rs_vers, check=c("pp_check", "reqq", "qq"))
```

#### Inspect interactions

```{r}
# get marginal means per group
mmeans <- emmeans(model3_control_rs_vers, specs = ~ condition|group, ref="Control", type="response")
mmeans

# contrasts between marginal means per group
contrasts <- contrast(mmeans, list(reward_control = c(1, 0, 0, 0, -1),
                                   policy_control = c(0, 0, 0, 1, -1)),
                      adjust="bonferroni")
contrasts


# get marginal means per version
mmeans <- emmeans(model3_control_rs_vers, specs = ~ condition|version, ref="Control", type="response")
mmeans

# contrasts between marginal means per version
contrasts <- contrast(mmeans, list(reward_control = c(1, 0, 0, 0, -1),
                                   goalstate_control = c(0, 1, 0, 0, -1),
                                   policy_control = c(0, 0, 0, 1, -1)),
                      adjust="bonferroni")
contrasts

```

# Time (trial) effects

```{r}
# Set contrasts
contrasts(trial_df$group) <- contr.sum(2)*-0.5
contrasts(trial_df$version) <- contr.sum(2)*-0.5
### contrast for condition changes from analysis to analysis

# Prepare LogReg dfs
logreg_test_path_group_version_condition_env_time_df_full <- trial_df %>%
  filter(phase == "test",
         state == 1) %>%
  mutate(switch_path = as.factor(switch_path),
         condition = as.factor(condition),
         version = as.factor(version),
         group = as.factor(group),
         environment = as.factor(environment),
         condition_index = as.factor(condition_index),
         trial = trial-1) %>%
  select(group,
         version,
         ID,
         switch_path,
         condition,
         condition_index,
         trial,
         environment)

logreg_test_path_condition_env_time_df_lowrisk_control <- trial_df %>%
  filter(phase == "test",
         state == 1,
         group == "Low-risk drinkers",
         version == "Monetary version") %>%
  mutate(switch_path = as.factor(switch_path),
         condition = as.factor(condition),
         environment = as.factor(environment),
         condition_index = as.factor(condition_index),
         trial = trial-1) %>%
  select(ID,
         switch_path,
         condition,
         condition_index,
         trial,
         environment)

logreg_test_path_group_condition_env_time_df_alcohol <- trial_df %>%
  filter(phase == "test",
         state == 1,
         version == "Alcohol version") %>%
  mutate(switch_path = as.factor(switch_path),
         condition = as.factor(condition),
         group = as.factor(group),
         environment = as.factor(environment),
         condition_index = as.factor(condition_index),
         trial = trial-1) %>%
  select(group,
         ID,
         switch_path,
         condition,
         condition_index,
         trial,
         environment)

```

### Plot

```{r}
test_path_group_version_condition_trial_df <- trial_df %>%
  filter(phase == "test",
         state == 1) %>%
  group_by(group, version, condition, trial) %>%
  summarise(mean_switch = mean(switch_path, na.rm = TRUE),
            se_switch = sd(switch_path, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(switch_path, na.rm=TRUE)[2],
            ci_u = ci(switch_path, na.rm=TRUE)[3],
            n = n()
            )

test_path_group_version_condition_trial_df %>%
  kable("html") %>%
  kable_styling(font_size = 18,
                latex_options = "scale_down")
```

```{r}
supp.labs<- c("Low-risk drinkers", "High-risk drinkers", "Non-alcohol context", "Alcohol context")
names(supp.labs) <- c("Low-risk drinkers", "Harmful drinkers", "Monetary version", "Alcohol version")

ggplot(test_path_group_version_condition_trial_df, aes(x=trial, y=mean_switch, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), aes(fill = condition)) +
  geom_errorbar(aes(ymin=mean_switch-se_switch, ymax=mean_switch+se_switch), width=.2, position=position_dodge(.9)) +
  scale_y_continuous(limits = c(-0.05, 1.05)) +
  facet_grid(vars(group), vars(version), labeller = as_labeller(supp.labs)) +
  theme_light(base_size = 16, base_family = "Aptos") +
  xlab("Test trial") +
  ylab("Proportion of trials \n with changed path preference") +
  guides(fill=guide_legend(title="Condition")) +
  theme(
        legend.position = "right",
        axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16),
        legend.text=element_text(size=16)) +
  scale_color_viridis(option = "viridis", discrete = TRUE) +
  scale_fill_viridis(option = "viridis", discrete = TRUE)

ggsave(filename = "suppl_trialeffects.png", path = figure_path, width = 11, height = 6, device='png', dpi=600)
```

### Logistic regression

#### Full dataset, compare against transition revaluation

```{r}
contrasts(logreg_test_path_group_version_condition_env_time_df_full$condition) <- contr.treatment(5, base = 3)

# model3_trial <- glmer(switch_path ~ group*version*condition*trial + (1 + condition | ID),
#                 data = logreg_test_path_group_version_condition_env_time_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model3_trial, file=file.path(model_path, "model3_trial_switch.rds"))
model3_trial <- readRDS(file.path(model_path, "model3_trial_switch.rds"))

# # does not converge
# model3_trial_rs <- glmer(switch_path ~ group*version*condition*trial + (1 + condition + trial | ID),
#                 data = logreg_test_path_group_version_condition_env_time_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model3_trial_rs, file=file.path(model_path, "model3_trial_rs_switch.rds"))
model3_trial_rs <- readRDS(file.path(model_path, "model3_trial_rs_switch.rds"))

anova(model3_trial, model3_trial_rs)

tab_model(model3_trial, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model3_trial, check=c("pp_check", "reqq", "qq"))
```

##### Inspect interactions

```{r}
# get marginal means per condition and version
mmeans <- emmeans(model3_trial, ~ condition|version, at = list(trial = 0), type="response")
mmeans

# contrasts between policy and transition slopes per group and version
contrasts <- contrast(mmeans, "trt.vs.ctrl", ref=3, adjust="bonferroni")
contrasts

# get marginal means per condition and group
mmeans <- emmeans(model3_trial, ~ condition|group, at = list(trial = 0), type="response")
mmeans

# contrasts between policy and transition slopes per group and version
contrasts <- contrast(mmeans, 
                      list(control_transition = c(0, 0, -1, 0, 1)),
                      adjust="bonferroni")
contrasts

# get trial slopes per condition and group
mmeans <- emtrends(model3_trial, ~ condition|group, var="trial")
mmeans

contrasts <- contrast(mmeans,
                      list(control_transition = c(0, 0, -1, 0, 1)),
                      adjust = "bonferroni")
contrasts
```

#### Full dataset, compare against control condition

```{r}
contrasts(logreg_test_path_group_version_condition_env_time_df_full$condition) <- contr.treatment(5, base = 5)

# model_control_trial <- glmer(switch_path ~ group*version*condition*trial + (1 + condition | ID),
#                 data = logreg_test_path_group_version_condition_env_time_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model_control_trial, file=file.path(model_path, "model_control_trial_switch.rds"))
model_control_trial <- readRDS(file.path(model_path, "model_control_trial_switch.rds"))

# does not converge
# model_control_trial_rs <- glmer(switch_path ~ group*version*condition*trial + (1 + condition + trial | ID),
#                 data = logreg_test_path_group_version_condition_env_time_df_full,
#                 family = "binomial",
#                 glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)))
# saveRDS(model_control_trial_rs, file=file.path(model_path, "model_control_trial_rs_switch.rds"))
model_control_trial_rs <- readRDS(file.path(model_path, "model_control_trial_rs_switch.rds"))

anova(model_control_trial, model_control_trial_rs)

tab_model(model_control_trial, show.est = T, show.stat = T, auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(model_control_trial, check=c("pp_check", "reqq", "qq"))
```

##### Inspect interactions

```{r}
# get contrasts between trial slopes per condition qnd group (compared to control)
mmeans <- emtrends(model_control_trial, ~ condition|group, var="trial")
test(mmeans)

contrasts <- contrast(mmeans,
                      list(reward_control = c(1, 0, 0, 0, -1),
                           goal_control = c(0, 1, 0, 0, -1),
                           policy_control = c(0, 0, 0, 1, -1)),
                      adjust="bonferroni")
contrasts

# get contrasts between trial slopes per condition and version (compared to control)
mmeans <- emtrends(model_control_trial, ~ condition|version, var="trial")

contrasts <- contrast(mmeans,
                      "trt.vs.ctrl", ref=5,
                      adjust=NULL)
contrasts

# get mmeans at first trial per condition and group
mmeans <- emmeans(model_control_trial, ~ condition|group, at = list(trial = 0), type="response")
mmeans

contrasts <- contrast(mmeans, "trt.vs.ctrl", ref=5, adjust="bonferroni")
contrasts

# get mmeans at first trial per condition and version
mmeans <- emmeans(model_control_trial, ~ condition|version, at = list(trial = 0), type="response")
mmeans

contrasts <- contrast(mmeans, "trt.vs.ctrl", ref=5, adjust=NULL)
contrasts
```

# Reaction times (all test-phase states)

## RT per condition

### Plot

```{r}
RT_test_condition_df <- trial_df %>%
  filter(phase == "test") %>%
  group_by(condition) %>%
  summarise(mean_RT = mean(RT),
            se_RT = sd(RT, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(RT, na.rm=TRUE)[2],
            ci_u = ci(RT, na.rm=TRUE)[3],
            n=n())

RT_test_condition_df %>%
  kable("html",
        digits=2) %>%
  kable_styling(font_size = 16,
                latex_options = "scale_down")


RT_test_condition_df_gc <- trial_df %>%
  filter(phase == "test") %>%
  group_by(group, version, condition) %>%
  summarise(mean_RT = mean(RT),
            se_RT = sd(RT, na.rm = TRUE)/sqrt(n()),
            ci_l = ci(RT, na.rm=TRUE)[2],
            ci_u = ci(RT, na.rm=TRUE)[3],
            n=n())

RT_test_condition_df_gc %>%
  kable("html",
        digits=2) %>%
  kable_styling(font_size = 16,
                latex_options = "scale_down")

```

```{r}

supp.labs <- c("Low-risk drinkers", "High-risk drinkers", "Non-alcohol context", "Alcohol context")
names(supp.labs) <- c("Low-risk drinkers", "Harmful drinkers", "Monetary version", "Alcohol version")

RT_test_plotting_df <- trial_df %>%
  filter(phase == "test")

ggplot(RT_test_plotting_df, aes(x=condition, y=RT, fill = condition)) +
  geom_violin(size=0.3, alpha=0.5) +
  geom_boxplot(size=0.3, width=0.2, outliers = F, alpha=0) +
  facet_grid(vars(group), vars(version), labeller = as_labeller(supp.labs)) +
  theme_light(base_size = 16, base_family = "Aptos") +
  xlab("Phase") +
  ylab("Response times (ms)") +
  ylim(c(0,12500)) +
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.text.x = element_text(angle = 50, vjust = 1, hjust=1, size=16),
        axis.text.y = element_text(size=16),
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16)) +
  scale_fill_viridis("Condition", option = "viridis", discrete = TRUE)

ggsave(filename = "suppl_RTs.png", path = figure_path, width = 8, height = 7, device='png', dpi=600)
```

### Linear regression

```{r}
# Set contrasts
contrasts(trial_df$group) <- contr.sum(2)*-0.5
contrasts(trial_df$version) <- contr.sum(2)*-0.5
### contrast for condition changes from analysis to analysis


linreg_test_rt_df <- trial_df %>%
  filter(phase == "test"
         ) %>%
  mutate(condition = as.factor(condition),
         group = as.factor(group),
         version = as.factor(version),
         environment = as.factor(environment)) %>%
  dplyr::select(ID,
         RT,
         condition,
         group,
         version,
         environment)


linreg_test_rt_lowrisk_control_df <- trial_df %>%
  filter(phase == "test",
         group == "Low-risk drinkers",
         version == "Monetary version"
         ) %>%
  mutate(condition = as.factor(condition),
         group = as.factor(group),
         version = as.factor(version),
         environment = as.factor(environment)) %>%
  dplyr::select(ID,
         RT,
         condition,
         group,
         version,
         environment)
```

#### Low-risk drinkers non-alcohol context, compare to transition revaluation

```{r}
contrasts(linreg_test_rt_lowrisk_control_df$condition) <- contr.treatment(5, base = 3)

rt_test_transition_lowrisk_control_model <- lmer(data = linreg_test_rt_lowrisk_control_df,
                                 RT ~ condition + (1 | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

rt_test_transition_lowrisk_control_model_rs <- lmer(data = linreg_test_rt_lowrisk_control_df,
                                 RT ~ condition + (1 + condition | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

anova(rt_test_transition_lowrisk_control_model, rt_test_transition_lowrisk_control_model_rs)

tab_model(rt_test_transition_lowrisk_control_model_rs, show.est = T, show.stat = T, show.df = T, df.method = "satterthwaite", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(rt_test_transition_lowrisk_control_model_rs, check=c("pp_check", "reqq", "qq"))

# rt_test_transition_lowrisk_control_model_rob <- rlmer(data = linreg_test_rt_lowrisk_control_df,
#                                  RT ~ condition + (1 | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
#saveRDS(rt_test_transition_lowrisk_control_model_rob, file=file.path(model_path, "rt_test_transition_lowrisk_control_model_rob.rds"))
rt_test_transition_lowrisk_control_model_rob <- readRDS(file.path(model_path, "rt_test_transition_lowrisk_control_model_rob.rds"))

# rt_test_transition_lowrisk_control_model_rs_rob <- rlmer(data = linreg_test_rt_lowrisk_control_df,
#                                  RT ~ condition + (1 + condition | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_transition_lowrisk_control_model_rs_rob, file=file.path(model_path, "rt_test_transition_lowrisk_control_model_rs_rob.rds"))
rt_test_transition_lowrisk_control_model_rs_rob <- readRDS(file.path(model_path, "rt_test_transition_lowrisk_control_model_rs_rob.rds"))

tab_model(rt_test_transition_lowrisk_control_model_rs_rob, show.est = T, show.stat = T, show.df = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

#confint<-confintROB(rt_test_transition_lowrisk_control_model_rs_rob, parm=c(1:5), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(confint, file=file.path(model_path, "confint_rt_test_transition_lowrisk_control_model_rs_rob.rds"))
confint <- readRDS(file.path(model_path, "confint_rt_test_transition_lowrisk_control_model_rs_rob.rds"))
confint
```

#### Low-risk drinkers non-alcohol context, compare to reward revaluation

```{r}
contrasts(linreg_test_rt_lowrisk_control_df$condition) <- contr.treatment(5, base = 1)

rt_test_reward_lowrisk_control_model <- lmer(data = linreg_test_rt_lowrisk_control_df,
                                 RT ~ condition + (1 | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

rt_test_reward_lowrisk_control_model_rs <- lmer(data = linreg_test_rt_lowrisk_control_df,
                                 RT ~ condition + (1 + condition | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

anova(rt_test_reward_lowrisk_control_model, rt_test_reward_lowrisk_control_model_rs)

tab_model(rt_test_reward_lowrisk_control_model_rs, show.est = T, show.stat = T, show.df = T, df.method = "satterthwaite", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(rt_test_reward_lowrisk_control_model_rs, check=c("pp_check", "reqq", "qq"))

# rt_test_reward_lowrisk_control_model_rob <- rlmer(data = linreg_test_rt_lowrisk_control_df,
#                                  RT ~ condition + (1 | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_reward_lowrisk_control_model_rob, file=file.path(model_path, "rt_test_reward_lowrisk_control_model_rob.rds"))
rt_test_reward_lowrisk_control_model_rob <- readRDS(file.path(model_path, "rt_test_reward_lowrisk_control_model_rob.rds"))

# rt_test_reward_lowrisk_control_model_rs_rob <- rlmer(data = linreg_test_rt_lowrisk_control_df,
#                                  RT ~ condition + (1 + condition | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_reward_lowrisk_control_model_rs_rob, file=file.path(model_path, "rt_test_reward_lowrisk_control_model_rs_rob.rds"))
rt_test_reward_lowrisk_control_model_rs_rob <- readRDS(file.path(model_path, "rt_test_reward_lowrisk_control_model_rs_rob.rds"))

tab_model(rt_test_reward_lowrisk_control_model_rs_rob, show.est = T, show.stat = T, show.df = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

#confint <- confintROB(rt_test_reward_lowrisk_control_model_rs_rob, parm=c(1:5), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(confint, file=file.path(model_path, "confint_rt_test_reward_lowrisk_control_model_rs_rob.rds"))
confint <- readRDS(file.path(model_path, "confint_rt_test_reward_lowrisk_control_model_rs_rob.rds"))
confint
```

#### Full sample, compare to transition revaluation

```{r}
contrasts(linreg_test_rt_df$condition) <- contr.treatment(5, base = 3)

rt_test_transition_model <- lmer(data = linreg_test_rt_df,
                                 RT ~ group*version*condition + (1 | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

rt_test_transition_model_rs <- lmer(data = linreg_test_rt_df,
                                 RT ~ group*version*condition + (1 + condition | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

anova(rt_test_transition_model, rt_test_transition_model_rs)

tab_model(rt_test_transition_model_rs, show.est = T, show.stat = T, show.df = T, df.method = "satterthwaite", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(rt_test_transition_model_rs, check=c("pp_check", "reqq", "qq"))

# rt_test_transition_model_rob <- rlmer(data = linreg_test_rt_df,
#                                  RT ~ group*version*condition + (1 | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_transition_model_rob, file=file.path(model_path, "rt_test_transition_model_rob.rds"))
rt_test_transition_model_rob <- readRDS(file.path(model_path, "rt_test_transition_model_rob.rds"))

# does not converge
# rt_test_transition_model_rs_rob <- rlmer(data = linreg_test_rt_df,
#                                  RT ~ group*version*condition + (1 + condition | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_transition_model_rs_rob, file=file.path(model_path, "rt_test_transition_model_rs_rob.rds"))

tab_model(rt_test_transition_model_rob, show.est = T, show.stat = T, show.df = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

#confint1<-confintROB(rt_test_transition_model_rob, parm=c(1:20), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(confint1, file=file.path(model_path, "confint_rt_test_transition_model_rs_rob.rds"))
confint1 <- readRDS(file.path(model_path, "confint_rt_test_transition_model_rs_rob.rds"))
confint1
```

#### Full sample, compare to reward revaluation

```{r}
contrasts(linreg_test_rt_df$condition) <- contr.treatment(5, base = 1)

rt_test_reward_model <- lmer(data = linreg_test_rt_df,
                                 RT ~ group*version*condition + (1 | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

# does not converge
rt_test_reward_model_rs <- lmer(data = linreg_test_rt_df,
                                 RT ~ group*version*condition + (1 + condition | ID),
                                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                                 REML = FALSE)

anova(rt_test_reward_model, rt_test_reward_model_rs)

tab_model(rt_test_reward_model_rs, show.est = T, show.stat = T, show.df = T, df.method = "satterthwaite", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

check_model(rt_test_reward_model_rs, check=c("pp_check", "reqq", "qq"))

# rt_test_reward_model_rob <- rlmer(data = linreg_test_rt_df,
#                                  RT ~ group*version*condition + (1 | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_reward_model_rob, file=file.path(model_path, "rt_test_reward_model_rob.rds"))
rt_test_reward_model_rob <- readRDS(file.path(model_path, "rt_test_reward_model_rob.rds"))

# rt_test_reward_model_rs_rob <- rlmer(data = linreg_test_rt_df,
#                                  RT ~ group*version*condition + (1 + condition | ID),
#                                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
#                                  REML = FALSE)
# saveRDS(rt_test_reward_model_rs_rob, file=file.path(model_path, "rt_test_reward_model_rs_rob.rds"))
rt_test_reward_model_rs_rob <- readRDS(file.path(model_path, "rt_test_reward_model_rs_rob.rds"))

tab_model(rt_test_reward_model_rs_rob, show.est = T, show.stat = T, show.df = T, df.method = "wald", auto.label = FALSE, CSS = list(css.table = '+font-size: 14;'))

#confint2<-confintROB(rt_test_reward_model_rob, parm=c(1:20), level=0.95, method="boot", boot.type = "parametric")
#saveRDS(confint2, file=file.path(model_path, "confint_rt_test_reward_model_rs_rob.rds"))
confint2 <- readRDS(file.path(model_path, "confint_rt_test_reward_model_rs_rob.rds"))
confint2

```

##### Inspect interactions

```{r}
# get marginal means per version
mmeans <- emmeans(rt_test_reward_model_rs, specs = ~ condition|version, type="response")
mmeans

contrasts <- contrast(mmeans,
                      "trt.vs.ctrl", ref=1,
                      adjust=NULL)
contrasts 
```
